---
output: github_document
---
  
<!-- 01_GetPartitions.md is generated from 01_GetPartitions.Rmd. Please edit that file -->
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

<!-- badges: start -->
  
<!-- badges: end -->
  
I want to create data tables containing all possible four-way partitions with $n=6, ..., 10$ taxa. The data table should contain the following columns:
  
-   set_i: taxa included in partition i of 4, separated by "\|"
-   allQuads: all quadruples possible with the given partition, separated by "\|"


According to Stirling numbers of the second kind, there are 34,105 different partitions for 10 taxa.

There are nine types of partitions:
  
1)  a \| b \| c \| defghij --> 6, 7, 8, 9, 10
2)  a \| b \| cd \| efghij --> 6, 7, 8, 9, 10
3)  a \| b \| cde \| fghij -->       8, 9, 10
4)  a \| b \| cdef \| ghij -->             10
5)  a \| bc \| de \| fghij -->    7, 8, 9, 10
6)  a \| bc \| def \| ghij -->          9, 10
7)  a \| bcd \| efg \| hij -->             10
8)  ab \| cd \| ef \| ghij -->       8, 9, 10
9)  ab \| cd \| efg \| hij -->             10


I create them separately and combine them at the end.

In addition, I test the table with some example data sets (not decisive: Mareikes Mathematica example, decisive: some trees added to the previous example)

# Initialize

```{r 01_init}
rm(list = ls())
time0<-Sys.time()

source("../helperFunctions/StirlingFunction.R")
source("../helperFunctions/PartitioningFunction.R")
source("../helperFunctions/PartitioningFunction_HelpR.R")
source("../SourceFile.R")

```

# Check & general parameters

```{r checkSterlingNumbers}
StirlingFunction(n=6,k=4)
StirlingFunction(n=7,k=4)
StirlingFunction(n=8,k=4)
StirlingFunction(n=9,k=4)
StirlingFunction(n=10,k=4)

```

# Set 1 (all n)

a \| b \| c \| def == 1 + 1 + 1 + 3
a \| b \| c \| defg == 1 + 1 + 1 + 4
a \| b \| c \| defgh == 1 + 1 + 1 + 5
a \| b \| c \| defghi == 1 + 1 + 1 + 6
a \| b \| c \| defghij == 1 + 1 + 1 + 7

```{r set1}
tab1_n6 = PartitioningFunction(1,1,1,3)
tab1_n7 = PartitioningFunction(1,1,1,4)
tab1_n8 = PartitioningFunction(1,1,1,5)
tab1_n9 = PartitioningFunction(1,1,1,6)
tab1_n10 = PartitioningFunction(1,1,1,7)

```

# Set 2 (all n)

a \| b \| cd \| ef == 1 + 1 + 2 + 2
a \| b \| cd \| efg == 1 + 1 + 2 + 3
a \| b \| cd \| efgh == 1 + 1 + 2 + 4
a \| b \| cd \| efghi == 1 + 1 + 2 + 5
a \| b \| cd \| efghij == 1 + 1 + 2 + 6

```{r set2}
tab2_n6 = PartitioningFunction(1,1,2,2)
tab2_n7 = PartitioningFunction(1,1,2,3)
tab2_n8 = PartitioningFunction(1,1,2,4)
tab2_n9 = PartitioningFunction(1,1,2,5)
tab2_n10 = PartitioningFunction(1,1,2,6)

```

# Set 3 (8, 9, 10)

a \| b \| cde \| fgh == 1 + 1 + 3 + 3
a \| b \| cde \| fghi == 1 + 1 + 3 + 4
a \| b \| cde \| fghij == 1 + 1 + 3 + 5

```{r set3}
tab3_n8 = PartitioningFunction(1,1,3,3)
tab3_n9 = PartitioningFunction(1,1,3,4)
tab3_n10 = PartitioningFunction(1,1,3,5)

```

# Set 4 (10)

a \| b \| cdef \| ghij == 1 + 1 + 4 + 4

```{r set4}
tab4_n10 = PartitioningFunction(1,1,4,4)

```

# Set 5 (7, 8, 9, 10)

a \| bc \| de \| fg == 1 + 2 + 2 + 2
a \| bc \| de \| fgh == 1 + 2 + 2 + 3
a \| bc \| de \| fghi == 1 + 2 + 2 + 4
a \| bc \| de \| fghij == 1 + 2 + 2 + 5

```{r set5}
tab5_n7 = PartitioningFunction(1,2,2,2)
tab5_n8 = PartitioningFunction(1,2,2,3)
tab5_n9 = PartitioningFunction(1,2,2,4)
tab5_n10 = PartitioningFunction(1,2,2,5)


```

# Set 6 (9, 10)

a \| bc \| def \| ghi == 1 + 2 + 3 + 3
a \| bc \| def \| ghij == 1 + 2 + 3 + 4

```{r set6}
tab6_n9 = PartitioningFunction(1,2,3,3)
tab6_n10 = PartitioningFunction(1,2,3,4)

```

# Set 7 (10)

a \| bcd \| efg \| hij == 1 + 3 + 3 + 3

```{r set7}
tab7_n10 = PartitioningFunction(1,3,3,3)


```

# Set 8 (8,9,10)

ab \| cd \| ef \| gh == 2 + 2 + 2 + 2
ab \| cd \| ef \| ghi == 2 + 2 + 2 + 3
ab \| cd \| ef \| ghij == 2 + 2 + 2 + 4

```{r set8}
tab8_n8 = PartitioningFunction(2,2,2,2)
tab8_n9 = PartitioningFunction(2,2,2,3)
tab8_n10 = PartitioningFunction(2,2,2,4)

```

# Set 9

ab \| bc \| efg \| hij == 2 + 2 + 3 + 3

```{r set9}
tab9_n10 = PartitioningFunction(2,2,3,3)

```

# Combine & Check

```{r combine}
myTab_n06 = rbind(tab1_n6,tab2_n6)
stopifnot(dim(myTab_n06)[1]==StirlingFunction(n=6,k=4))

myTab_n07 = rbind(tab1_n7,tab2_n7,tab5_n7)
stopifnot(dim(myTab_n07)[1]==StirlingFunction(n=7,k=4))

myTab_n08 = rbind(tab1_n8,tab2_n8,tab3_n8,tab5_n8,tab8_n8)
stopifnot(dim(myTab_n08)[1]==StirlingFunction(n=8,k=4))

myTab_n09 = rbind(tab1_n9,tab2_n9,tab3_n9,tab5_n9,tab6_n9,tab8_n9)
stopifnot(dim(myTab_n09)[1]==StirlingFunction(n=9,k=4))

myTab_n10 = rbind(tab1_n10,tab2_n10,tab3_n10,tab4_n10,
                  tab5_n10,tab6_n10,tab7_n10,tab8_n10,tab9_n10)
stopifnot(dim(myTab_n10)[1]==StirlingFunction(n=10,k=4))


```

# Save

```{r save}
save(myTab_n06,file = "../results/01_partitions/partitions_n06.RData")
save(myTab_n07,file = "../results/01_partitions/partitions_n07.RData")
save(myTab_n08,file = "../results/01_partitions/partitions_n08.RData")
save(myTab_n09,file = "../results/01_partitions/partitions_n09.RData")
save(myTab_n10,file = "../results/01_partitions/partitions_n10.RData")

```

# Session Info

```{r}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "mins"),3)," minutes")

```
