---
title: "Evaluation 1: get test properties"
author: "Janne Pott"
date: "13/03/2023"
output: pdf_document
---

<!-- 03_1_EvaluationTest.md is generated from 03_1_EvaluationTest.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Summary of Simulations

<!-- badges: start -->

<!-- badges: end -->

What did I simulate?

**Preparation**: create all possible quadruples and all possible 4-way partitions (4WP) for $n=6, ..., 10$ taxa

**Simulation**: for $n$ taxa, there are $K_n=\binom{n}{4}$ possible quadruples. For each $k \in \{1, ..., K_n\}$, there are $M_k=\binom{K_n}{k}$ combinations of quadruples as input and 10,000 of these $M_k$ combinations are used in the simulation. Each combination is tested for phylogenetic decisiveness according to 4WPP (truth) and fixing tacon traceability (test). 

**Here**: Summary of the simulation results (barplots, negative predictive value, power). 
 
Upper bound: it was already shown that given an input of $\binom{n}{4} - (n-4)$ quadruples, all sets are phylogenetic decisive: 
 
* $n=6$: $15-2 = 13$
* $n=7$: $35-3 = 32$
* $n=8$: $70-4 = 66$
* $n=9$: $126-5 = 121$
* $n=10$: $210-6 = 204$

Lower bound: the minimal triple covering, $\frac{1}{4}\binom{n}{3}$:
 
* $n=6$: 5
* $n=7$: 9
* $n=8$: 14
* $n=9$: 21
* $n=10$: 30
 
# Initialize

I use a file names *SourceFile.R* that contains all relevant R packages and user-/server-specific path to the R library. If using this code, you must make all the necessary changes within the template source file. 

```{r init}
rm(list = ls())
time0<-Sys.time()

source("../SourceFile.R")
source("../helperFunctions/TestHelpRFunction.R")
source("../helperFunctions/ShiftLegendBarplot.R")

x_lowerBound = c()
x_upperBound = c()

for(i in 6:10){
  #i=7
  min_quad = choose(i,3)/4
  x_lowerBound = c(x_lowerBound,ceiling(min_quad))
  max_quad = choose(i,4) - (i-4)
  x_upperBound = c(x_upperBound,max_quad)
}

```

# Get data

```{r input}
load("../results/02_SimulationResults_n06.RData")
load("../results/02_SimulationResults_n07.RData")
load("../results/02_SimulationResults_n08.RData")
load("../results/02_SimulationResults_n09.RData")
load("../results/02_SimulationResults_n10.RData")

SimulationResults_n06[,n := 6]
SimulationResults_n07[,n := 7]
SimulationResults_n08[,n := 8]
SimulationResults_n09[,n := 9]
SimulationResults_n10[,n := 10]

sim_n6 = SimulationResults_n06[k>=x_lowerBound[1] & k<=x_upperBound[1]]
sim_n7 = SimulationResults_n07[k>=x_lowerBound[2] & k<=x_upperBound[2]]
sim_n8 = SimulationResults_n08[k>=x_lowerBound[3] & k<=x_upperBound[3]]
sim_n9 = SimulationResults_n09[k>=x_lowerBound[4] & k<=x_upperBound[4]]
sim_n10 = SimulationResults_n10[k>=x_lowerBound[5] & k<=x_upperBound[5]]

sim = rbind(sim_n6,sim_n7,sim_n8,sim_n9,sim_n10)
table(sim$n)

```

# Bar plots

```{r barplots}
dumTab1 = foreach(i = 6:10)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  x1 = dim(mySim)[1]
  
  PlotData = data.table(n = i, 
                        k = rep(mySim$k,2),
                        phyloDec = c(mySim$NR_FTT,mySim$NR_PhyloDec),
                        category = c(rep("FTT",x1),rep("4WPP",x1)))
  ggplot(data=PlotData,aes(fill=category, y=phyloDec, x=k)) + 
    geom_bar(position="dodge", stat="identity")
  
  PlotData
}
BarPlotData = rbindlist(dumTab1)

p1 = ggplot(data=BarPlotData,aes(fill=category, y=phyloDec, x=k)) + 
  facet_wrap(vars(n), nrow = 2, scales = "free") +
  geom_bar(position="dodge", stat="identity") + 
  labs(x="Number of input quadruples                        ",
       y = "Correct identification",
       color = "Legend") + 
  scale_color_manual(values = c("darkblue","orange"),
                     labels = c("Four-way partition property",
                                "Fixing taxon traceable"))
grid.draw(ShiftLegendBarplot(p1))

```

# Line plots

```{r lineplots}
dumTab2 = foreach(i=6:10)%do%{
  #i=6
  dum = choose(i,4)
  dum2 = copy(sim)
  dum2 = dum2[n==i]
  dum2[,prop_4WPP := NR_PhyloDec/(NR_PhyloDec + NR_NotPhyloDec)]
  dum2[,prop_FTT := NR_FTT/(NR_PhyloDec + NR_NotPhyloDec)]
  #dum2 = dum2[!is.na(posRate)]
  dum2[,k2 := k/dum]
  dum2
}
LinePlotData2 = rbindlist(dumTab2)

dumTab3 = foreach(i=6:10)%do%{
  #i=6
  dum = choose(i,4)
  x = choose(i-1,3)-1
  y = x/dum
  a = choose(i,4) - (3*i-13)
  b = a/dum
  
  dum2 = copy(sim)
  dum2 = dum2[!is.na(posRate)]
  dum2 = dum2[n==i]
  dum2 = dum2[posRate==1,]
  v = min(dum2$k)
  w = v/dum
  res = data.table(n=i, vline1_abs = x, vline2_abs = a, vline3_abs = v, 
                   vline1_rel = y, vline2_rel = b, vline3_rel = w)
}
data_vline = rbindlist(dumTab3)

p2 <- ggplot(LinePlotData2[!is.na(posRate),]) +
  geom_line(aes(x=k, y=prop_FTT, col=as.factor(1)),linewidth=1,alpha=0.5) +
  geom_line(aes(x=k, y=prop_4WPP,col=as.factor(2)),linewidth=1,alpha=0.5)+
  geom_vline(data = data_vline,aes(xintercept = vline1_abs,col =as.factor(3))) +
  geom_vline(data = data_vline,aes(xintercept = vline2_abs,col =as.factor(4))) +
  geom_vline(data = data_vline,aes(xintercept = vline3_abs,col =as.factor(5))) +
  facet_wrap(~ n, nrow = 3, scales = "free_x",strip.position = "top") +
  theme(strip.background = element_blank(), 
        strip.placement = "outside")+
  labs(x="Number of input quadruples                                            ", 
       y = "Proportion of correct identification",
       color = "Legend") + 
  scale_color_manual(values = c("darkblue","orange","darkgreen","darkred","lightblue"),
                     labels = c("Proportion of phylo. dec. sets",
                                "Proportion of FTT sets",
                                "Lower bound of FTT",
                                "Upper bound of FTT",
                                "Upper bound of FTT (sim)"))
#,"upper bound","upper bound (simulation)"


grid.draw(ShiftLegendBarplot(p2))


```

#  Contingency tables (overall)

* Prevalence = actual positive (P) / all (N+P)
* PPV = Positive Predictive Value = true positives (TP) / predicted positives (PP) = conditional probability P(true state positive | prediction positive)
* NPV = Negative Predictive Value = true negatives (TN) / predicted negatives = conditional probability P(true state negative | prediction negative)
* TPR = True Positive Rate = sensitivity = power = TP / P
* TNR = True Negative Rate = specificity = TN / N
* see also [Wikipedia](https://en.wikipedia.org/wiki/Positive_and_negative_predictive_values)


```{r  contingencyTables1, eval=TRUE}
dumTab2 = foreach(i = 6:10)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  stats = TestHelpRFunction(P = sum(mySim$NR_PhyloDec),
                        N = sum(mySim$NR_NotPhyloDec),
                        PP = sum(mySim$NR_FTT))
  stats[,n:=i]
  stats
}
myStats = rbindlist(dumTab2)
myStats

```

**Fazit 1**: NPV is about 98%, i.e. there is a 98% probability that a negative set is really not phylogenically decisive 
 
**Fazit 2**: The power of the algorithm (TPR) is also about 98%. 

#  Contingency tables (per k)

```{r contingencyTables2}
dumTab3 = foreach(i = 6:10)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  
  dumTab4 = foreach(k = 1:dim(mySim)[1])%do%{
    # k=1
    myRow = copy(mySim)
    myRow = myRow[k,]
    
    stats_k = TestHelpRFunction(P = myRow$NR_PhyloDec,
                            N = myRow$NR_NotPhyloDec,
                            PP = myRow$NR_FTT)
    stats_k[,n :=i]
    stats_k[,k := myRow$k]
    stats_k
  }
  myStats_k = rbindlist(dumTab4)
  myStats_k
}
myStats_k = rbindlist(dumTab3)

filt_TPR = !is.na(myStats_k$TPR)
filt_NPV = !is.na(myStats_k$NPV)

boxplot(myStats_k$TPR[filt_TPR] ~ myStats_k$n[filt_TPR],
        xlab = "number of taxa",
        ylab = "power")
boxplot(myStats_k$NPV[filt_NPV] ~ myStats_k$n[filt_NPV],
        xlab = "number of taxa",
        ylab = "NPV")

tab6 = myStats_k[n==6 & filt_TPR,summary(TPR)]
tab7 = myStats_k[n==7 & filt_TPR,summary(TPR)]
tab8 = myStats_k[n==8 & filt_TPR,summary(TPR)]
tab9 = myStats_k[n==9 & filt_TPR,summary(TPR)]
tab10 = myStats_k[n==10 & filt_TPR,summary(TPR)]
tab_TPR = rbind(tab6,tab7,tab8,tab9,tab10)

tab6 = myStats_k[n==6 & filt_NPV,summary(NPV)]
tab7 = myStats_k[n==7 & filt_NPV,summary(NPV)]
tab8 = myStats_k[n==8 & filt_NPV,summary(NPV)]
tab9 = myStats_k[n==9 & filt_NPV,summary(NPV)]
tab10 = myStats_k[n==10 & filt_NPV,summary(NPV)]
tab_NPV = rbind(tab6,tab7,tab8,tab9,tab10)

tab6 = myStats_k[n==6 & Prevalence!=0,summary(Prevalence)]
tab7 = myStats_k[n==7 & Prevalence!=0,summary(Prevalence)]
tab8 = myStats_k[n==8 & Prevalence!=0,summary(Prevalence)]
tab9 = myStats_k[n==9 & Prevalence!=0,summary(Prevalence)]
tab10 = myStats_k[n==10 & Prevalence!=0,summary(Prevalence)]
tab_Prev = rbind(tab6,tab7,tab8,tab9,tab10)

tabs = as.data.table(rbind(tab_Prev,tab_NPV,tab_TPR))
tabs[,n:=rep(c(6:10),3)]
tabs[,Parameter:=c(rep("Prev",5),rep("NPV",5),rep("TPR",5))]
tabs = tabs[,c(8,7,1:6)]
tabs

# Plotting
LinePlotData3 = copy(myStats_k)
LinePlotData3 = LinePlotData3[!is.na(PPV)]

# Plot with colors
p3 <- ggplot(LinePlotData3) +
  geom_line(aes(x=k, y=Prevalence,col=as.factor(3)),linewidth=1,alpha=0.5)+
  geom_line(aes(x=k, y=NPV, col=as.factor(1)),linewidth=1,alpha=0.5) +
  geom_line(aes(x=k, y=TPR,col=as.factor(2)),linewidth=1,alpha=0.5)+
  facet_wrap(~ n, nrow = 3, scales = "free_x",strip.position = "top") +
  theme(strip.background = element_blank(), 
        strip.placement = "outside")+
  labs(x="Number of input quadruples                                            ",
       y = "",
       color = "Legend") + 
  scale_color_manual(values = c("darkblue","orange","darkgreen"),
                     labels = c("Negative Predictive Value",
                                "True Positive Rate (Power)",
                                "Prevalence"))
grid.draw(ShiftLegendBarplot(p3))

# Plot with line types
melt_data <- melt(LinePlotData3, id = c("n","k"),measure.vars = c("Prevalence","NPV","TPR")) 
melt_data[variable=="NPV",variable := "Negative Predictive Value"]
melt_data[variable=="TPR",variable := "True Positive Rate (Power)"]

p3 <- ggplot(melt_data,aes(x=k, y=value, group=variable)) +
  facet_wrap(~ n, 
             nrow = 3, 
             scales = "free_x",
             strip.position = "top",
             labeller=label_both) +
  geom_line(aes(linetype=variable),linewidth=1,alpha=0.75)+
  theme(strip.background = element_blank(), 
        strip.placement = "outside")+
  labs(x="Number of input quadruples                                            ",
       y = "",
       linetype = "Legend") 
grid.draw(ShiftLegendBarplot(p3))


test = copy(LinePlotData3)[TPR>0.9,]
test = test[!duplicated(n)] 
test[,allQ := choose(n,4)]
test[,prop := k/allQ]
test
```

# Some total numbers

```{r}
sumSim = sum(sim$NR_NotPhyloDec,sim$NR_PhyloDec)
sumPhyloDec = sum(sim$NR_PhyloDec)
sumFTT = sum(sim$NR_FTT)

sumPhyloDec/sumSim

sumFTT/sumPhyloDec

```

# Session Info

```{r sessionInfo}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "mins"),3)," minutes")

```
