---
title: "Evaluation 2: get table 1"
author: "Janne Pott"
date: "13/03/2023"
output: pdf_document
---

<!-- 03_2_GetTables.md is generated from 03_2_GetTables.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

In our manuscript, we present the summary of the simulation study in Table 1. In part, this was done before, but here I want to present it a bit nicer. This includes for all analyzed $n$ over all tested $k$ with at least one phylogenetic set:

* Prevalence of phylogenetic decisive sets in simulation (overall, min, max)
* True Positive Rate (TPR, sensitivity, power) (overall, min, max)
* Negative Predictive Value (NPV) (overall, min, max)
* Minimal set size satisfying the 4-way partition property (4WPP) in the simulation 
* Minimal set size which is fixing taxon traceable (FTT) in the simulation

In addition, I want a second table with more number, not necessarily out of the simulation

* Minimal set size satisfying the 4-way partition property
* Maximal set size not satisfying the 4-way partition property
* Minimal set size which is fixing taxon traceable
* Maximal set size which satisfy the 4-way partition property but is not fixing taxon traceable

# Initialize

I use a file names *SourceFile.R* that contains all relevant R packages and user-/server-specific path to the R library. If using this code, you must make all the necessary changes within the template source file. 

```{r init}
rm(list = ls())
time0<-Sys.time()

source("../SourceFile.R")
source("../helperFunctions/TestHelpRFunction.R")

x_lowerBound = c()
x_upperBound = c()

for(i in 6:10){
  #i=7
  y = i %% 6
  
  if(y==0){
    min_quad = 0.25 * choose(i,3) + i/6
  }else if(y %in% c(2,4)){
    min_quad = 0.25 * choose(i,3)
  }else{
    min_quad = (1/6) * ((i-1)/2) * choose(i,2) + i/12
    min_quad = ceiling(min_quad)
  }
  x_lowerBound = c(x_lowerBound,min_quad)
  max_quad = choose(i,4) - (i-4)
  x_upperBound = c(x_upperBound,max_quad)
}

load("../results/02_SimulationResults_n06.RData")
load("../results/02_SimulationResults_n07.RData")
load("../results/02_SimulationResults_n08.RData")
load("../results/02_SimulationResults_n09.RData")
load("../results/02_SimulationResults_n10.RData")

SimulationResults_n06[,n := 6]
SimulationResults_n07[,n := 7]
SimulationResults_n08[,n := 8]
SimulationResults_n09[,n := 9]
SimulationResults_n10[,n := 10]

sim_n6 = SimulationResults_n06[k>=x_lowerBound[1] & k<=x_upperBound[1]]
sim_n7 = SimulationResults_n07[k>=x_lowerBound[2] & k<=x_upperBound[2]]
sim_n8 = SimulationResults_n08[k>=x_lowerBound[3] & k<=x_upperBound[3]]
sim_n9 = SimulationResults_n09[k>=x_lowerBound[4] & k<=x_upperBound[4]]
sim_n10 = SimulationResults_n10[k>=x_lowerBound[5] & k<=x_upperBound[5]]

sim = rbind(sim_n6,sim_n7,sim_n8,sim_n9,sim_n10)
table(sim$n)

```

# Get Table 1

```{r  contingencyTables1, eval=TRUE}
dumTab2 = foreach(i = 6:10)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  stats = TestHelpRFunction(P = sum(mySim$NR_PhyloDec),
                        N = sum(mySim$NR_NotPhyloDec),
                        PP = sum(mySim$NR_FTT))
  stats[,n:=i]
  stats
}
myStats = rbindlist(dumTab2)
myStats

dumTab3 = foreach(i = 6:10)%do%{
  # i=6
  mySim = copy(sim)
  mySim = mySim[n == i,]
  
  dumTab4 = foreach(k = 1:dim(mySim)[1])%do%{
    # k=1
    myRow = copy(mySim)
    myRow = myRow[k,]
    
    stats_k = TestHelpRFunction(P = myRow$NR_PhyloDec,
                            N = myRow$NR_NotPhyloDec,
                            PP = myRow$NR_FTT)
    stats_k[,n :=i]
    stats_k[,k := myRow$k]
    stats_k
  }
  myStats_k = rbindlist(dumTab4)
  myStats_k
}
myStats_k = rbindlist(dumTab3)

x1 = myStats_k[Prevalence!=0,min(k),by = n]
x2 = myStats_k[Prevalence!=0 & TPR>0,min(k),by = n]

tab1 = copy(x1)
setnames(tab1,"V1","k_min_4WPP")
tab1[,k_min_FTT := x2$V1]

filt_TPR = !is.na(myStats_k$TPR)
tab6 = myStats_k[n==6 & filt_TPR,summary(TPR)]
tab7 = myStats_k[n==7 & filt_TPR,summary(TPR)]
tab8 = myStats_k[n==8 & filt_TPR,summary(TPR)]
tab9 = myStats_k[n==9 & filt_TPR,summary(TPR)]
tab10 = myStats_k[n==10 & filt_TPR,summary(TPR)]
tab_TPR = rbind(tab6,tab7,tab8,tab9,tab10)
tab1[,TPR := signif(tab_TPR[,3],2)]
tab1[,TPR_IQR := paste0("[",signif(tab_TPR[,2],2),",",signif(tab_TPR[,5],2),"]")]

filt_NPV = !is.na(myStats_k$NPV)
tab6 = myStats_k[n==6 & filt_NPV,summary(NPV)]
tab7 = myStats_k[n==7 & filt_NPV,summary(NPV)]
tab8 = myStats_k[n==8 & filt_NPV,summary(NPV)]
tab9 = myStats_k[n==9 & filt_NPV,summary(NPV)]
tab10 = myStats_k[n==10 & filt_NPV,summary(NPV)]
tab_NPV = rbind(tab6,tab7,tab8,tab9,tab10)
tab1[,NPV := signif(tab_NPV[,3],2)]
tab1[,NPV_IQR := paste0("[",signif(tab_NPV[,2],2),",",signif(tab_NPV[,5],2),"]")]

tab6 = myStats_k[n==6 & Prevalence!=0,summary(Prevalence)]
tab7 = myStats_k[n==7 & Prevalence!=0,summary(Prevalence)]
tab8 = myStats_k[n==8 & Prevalence!=0,summary(Prevalence)]
tab9 = myStats_k[n==9 & Prevalence!=0,summary(Prevalence)]
tab10 = myStats_k[n==10 & Prevalence!=0,summary(Prevalence)]
tab_Prev = rbind(tab6,tab7,tab8,tab9,tab10)
tab1[,Prev := signif(tab_Prev[,3],2)]
tab1[,Prev_IQR := paste0("[",signif(tab_Prev[,2],2),",",signif(tab_Prev[,5],2),"]")]
tab1
knitr::kable(tab1)
```

# Get Table 2

* Minimal set size satisfying the 4-way partition property
* Maximal set size not satisfying the 4-way partition property
* Minimal set size which is fixing taxon traceable
* Maximal set size which satisfy the 4-way partition property but is not fixing taxon traceable

```{r}
x1 = myStats_k[Prevalence!=0,min(k),by = n]
y1 = myStats_k[Prevalence<1,max(k),by = n]
x2 = myStats_k[Prevalence!=0 & TPR>0,min(k),by = n]
y2 = sim[posRate<1,max(k),by = n]

y3 = c()
for(i in 6:10){
  #i=6
  dum = choose(i,4) - 3*i +13
  y3[i-5]=dum
}

tab2 = copy(x1)
setnames(tab2,"V1","k_min_4WPP")
tab2[,k_max_4WPP_sim := y1$V1]
tab2[,k_max_4WPP_theo := x_upperBound-1]
tab2[,k_min_FTT := x2$V1]
tab2[,k_max_diff_sim := y2$V1]
tab2[,k_max_diff_theo := y3]

tab2 = t(tab2)
knitr::kable(tab2)



```

# Session Info

```{r sessionInfo}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "mins"),3)," minutes")

```
