---
title: "Evaluation 4: get tight upper bound"
subtitle: "Simulation evaluation"
author: "Janne Pott"
date: "`r Sys.Date()`"
output: github_document
---  

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The upper bound not decisive sets is given as

$$\binom{n}{4} - (n-4)+1 $$

E.g., for $n=6$, the bound is $\binom{6}{4} - 3 = 12$, so there are sets of size 12 which are neither decisive nor fixing taxon traceable. Here I just want to check if this bound is always met. 

(In the simulation, we did not test all possible combinations for the maximal $k_n$, hence we might have missed those sets in the direct test, but tested them with a lower starting $k$ with additional resolved quadruples.)


```{r setup}
rm(list = ls())
time0<-Sys.time()

source("../SourceFile.R")

```

# Load data

```{r load}
load("../results/02_SimulationResults_n06.RData")
load("../results/02_SimulationResults_n07.RData")
load("../results/02_SimulationResults_n08.RData")
load("../results/02_SimulationResults_n09.RData")
load("../results/02_SimulationResults_n10.RData")

SimulationResults_n06[,n := 6]
SimulationResults_n07[,n := 7]
SimulationResults_n08[,n := 8]
SimulationResults_n09[,n := 9]
SimulationResults_n10[,n := 10]

sim = rbind(SimulationResults_n06,SimulationResults_n07,SimulationResults_n08,SimulationResults_n09,SimulationResults_n10)
Sim = copy(sim)

dumTab = foreach(i=1:dim(Sim)[1])%do%{
  #i=357
  myRow = Sim[i,]
  myk = myRow$k
  myn = myRow$n
  
  if(myn<10){
      filefn = paste0("../results/02_SimulationsData_n0",myn,"/SimulationResults_n",myn,"_k",myk,"_rep10000.RData")
  }else{
      filefn = paste0("../results/02_SimulationsData_n",myn,"/SimulationResults_n",myn,"_k",myk,"_rep10000.RData")
  }
  load(filefn)
  myTest = myTest[FWPP == "NOT PhyloDec",]
  if(dim(myTest)[1]==0){
    res = data.table(n=myn, 
                     k=myk, 
                     FWPP = T, 
                     FixingTaxa = T,
                     input = NA)
  }else{
    res = data.table(n=myn, 
                     k=myk, 
                     FWPP = F, 
                     FixingTaxa = F,
               input = myTest$input)

      }
  res
}

PhyloDecSets_notFTT = rbindlist(dumTab)
PhyloDecSets_notFTT[,table(n,FWPP)]
PhyloDecSets_notFTT = PhyloDecSets_notFTT[FWPP==F,]

```

# Test data 

I want to test if I have sets starting with some input $k$ and ending with additional resolved quadruples so that the sum of input and solved quadruples equals the tight bound. 

```{r test}
dumTab = foreach(i = 6:10)%do%{
  #i=6
  dumTab1 = copy(PhyloDecSets_notFTT)
  dumTab1 = dumTab1[n==i,]
  
  setorder(dumTab1,-k)
  
  tracer = FALSE
  theo_threshold = choose(i,4) - (i-3)
    
  while(tracer == F & dim(dumTab1)[1]>0){
    dumTab2 = dumTab1[1,]
    myInput = dumTab1[1,input]
    myInput = unlist(strsplit(myInput,split = "[|]"))
    myOutput = data.table(myInput = myInput)
    myFn = paste0("../results/03_4_GetUpperBound/Example.txt")
    fwrite(myOutput,file=myFn,col.names = F)
    TestData = FTT_createInput(fn = myFn, sepSym = "_",c = 4)
    TestFTT = FTT_algorithmRed(data=TestData$data,
                               verbose = F,c = 4,n = myRow$n)
        
    testStatus = TestFTT[,.N,by=status]
    sim_res = testStatus[status != "unresolved",sum(N)]
    
    if(theo_threshold == sim_res){
        myResult = dumTab1[1,]
        myResult[,green := sim_res]
        myResult[,rounds := max(TestFTT$round)]
        print(myResult)
        myResult
        tracer = TRUE
    }else{
      dumTab1 = dumTab1[-1,]
    }
  }
  myResult
}

myResult = rbindlist(dumTab)
myResult[,c(1,2,6,7)]
save(myResult,file = "../results/03_4_UpperBound.RData")

```

Okay, it worked :)

# Session Info

```{r sessionInfo}
sessionInfo()
message("\nTOTAL TIME : " ,round(difftime(Sys.time(),time0,units = "mins"),3)," minutes")

```


